Oral anticoagulants

### 2020-12-16 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
typos

## Sort into monthly count data
oac_p_monthly_count <- oac_p %>% 
  group_by(datename, bnfchem) %>% 
  summarise(n = sum(Quantity)) %>% 
  mutate(n = n / sum(n)) %>% 
  filter(bnfchem == warf) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>%
    as_tsibble(index = datename)
```

```{r prep-data}

@@

oac_p_monthly_quantity_cluster <- 
  right_join(oac_p, select(gp, c(practiceid, cluster)), 
             by = c("PracticeID" = "practiceid")) %>%
  propRegional(cluster, datename, Quantity) %>% 
  left_join(gp %>% 
  select(c(practiceid, npat, cluster)) %>% 
  group_by(cluster) %>% 
  summarise(npat = sum(npat)), by = c("regional_unit" = "cluster")) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

oac_p_monthly_quantity_gp <- 
  propRegional(oac_p, PracticeID, datename, Quantity) %>% 
  right_join(select(gp, c(practiceid, npat)), 
            by = c("regional_unit" = "practiceid")) %>% 
  mutate(n = 1000*n/npat)

>>>>

## Sort into monthly count data
oac_p_monthly_count <- oac_p %>% 
  group_by(datename, bnfchem) %>% 
  summarise(n = sum(Quantity)) %>% 
  mutate(n = n / sum(n)) %>% 
  filter(bnfchem == warf) %>% 
  mutate(datename = yearmonth(datename),
         n = case_when(str_detect(datename, pattern = "Jan") ~ n/31,
                       str_detect(datename, pattern = "Feb") ~ n/28.25,
                       str_detect(datename, pattern = "Mar") ~ n/31,
                       str_detect(datename, pattern = "Apr") ~ n/30,
                       str_detect(datename, pattern = "May") ~ n/31,
                       str_detect(datename, pattern = "Jun") ~ n/30,
                       str_detect(datename, pattern = "Jul") ~ n/31,
                       str_detect(datename, pattern = "Aug") ~ n/31,
                       str_detect(datename, pattern = "Sep") ~ n/30,
                       str_detect(datename, pattern = "Oct") ~ n/31,
                       str_detect(datename, pattern = "Nov") ~ n/30,
                       str_detect(datename, pattern = "Dec") ~ n/31)) %>% 
  ungroup() %>%
    as_tsibble(index = datename)

@@

oac_p_monthly_quantity_cluster <- 
  right_join(oac_p, select(gp, c(practiceid, cluster)), 
             by = c("PracticeID" = "practiceid")) %>%
  propRegional(cluster, datename, Quantity, bnf = warf) %>% 
  left_join(gp %>% 
  select(c(practiceid, npat, cluster)) %>% 
  group_by(cluster) %>% 
  summarise(npat = sum(npat)), by = c("regional_unit" = "cluster")) %>% 
  mutate(n = 1000*n/npat) # quantity per 1000 pts

oac_p_monthly_quantity_gp <- 
  propRegional(oac_p, PracticeID, datename, Quantity, bnf = warf) %>% 
  right_join(select(gp, c(practiceid, npat)), 
            by = c("regional_unit" = "practiceid")) %>% 
  mutate(n = 1000*n/npat)
